% !TeX root = Bericht.tex
% !TeX spellcheck = en_US
\section{personal outlook}
Lastly, I would like to give a brief outlook onto my further university studies. I just finished my first semester in the physics master program and so far I quite enjoy the freedom of choice regarding the courses. It not only allows me but also motivates me to explore my interests in various fields of physics. So far I have attended a healthy mix of experimental, data analysis and theory courses and I have found out one thing: I am not a theorist. Although I enjoy the concepts of theoretical physics the maths involved is not my thing. I have always been quite fond of (extragalactic) astrophysics as the night sky is just marvelous to look at and hosts many unanswered questions. This led me to write my high school thesis on Quasars and observable phenomena (Jets, apparent superluminal velocities, gravitational lensing). During my undergraduate degree, I really valued the lab courses as they allowed me to apply my passion for data analysis in practice, offering a welcome balance to the otherwise dry and theoretical curriculum.

For this reason I chose to write my bachelor thesis in the institute of experimental physics under the supervision of Prof. Kirchmair. In my thesis I combined measurements from the lab with electromagnetic simulations to extract the origin and relative magnitude of losses in microwave resonators. This is as the uncovers the connection between manufacturing defects and coherence times in superconducting circuits. Even though the involved physics was not the most interesting, I got to manufacture the samples in the cleanroom, perform the measurements in the lab, set the simulations up and lastly analyze and compare the collected data. As a whole it was a really enjoyable and motivating experience as the tasks to perform were quite diverse and I had the feeling the work I was doing is of actual interest to the research group. For this reason I will probably also write my master thesis in the same research group as no other group (to my knowledge) offers the same level of diversity.

Next semester, I plan to attend a mix of different courses with a slight bias towards quantum engineering, as this knowledge will help me in my thesis. Looking further as the masters degree I could see myself doing a PhD and stay in academia after that as the idea of research and education is appealing to me. 