\documentclass{alex_summary}

\begin{document}
	\section{Block A}
	\subsection*{1}
	\begin{itemize}
		\item Which 4 groups did the EU decide to pick for categorizing quantum technologies?
		\item Which one do you believe is expected to be market-ready the earliest? Why?
		\item Make an estimate: what do you believe is easier to fabricate? Atoms, photons, or solid state systems?
		\item Make an estimate: what do you believe is easier/better to control? Atoms/ions, photons, or solid state systems?
	\end{itemize}
		
	\subsection*{2 + 3}
	\begin{itemize}
		\item What is an MVP?
		A minimum viable product is a cut-down version of the finished product. The aim is to release something on the market and get early feedback/insights to help in shaping the final product.
		\item What’s a user-story? How does it help?
		talk with your customers and get crucial feedback for the development process
		\item Name two locations to search for patents, check for patent families, and learn about the legal status?
		patents.google.com and Espacenet
		\item What are patent classes?
		Patent are categorized according to their belonging
		\item How long can a patent run at most?
		20 Years from the filing date
		\item What’s that grace period? Can you use it in Austria?
		Timeframe before filing a patent in which your product can make a public appearance (eg conference). In austria there is no grace period so the product of the patent has to be completely new to the public.
	\end{itemize}
	
	\subsection*{4}
	\begin{itemize}
		\item What efficient way can you envision to make your product RoHS compliant?
		Only buy stuff that already is RoHS compliant. Dont let companies use the excuse that its for scientific purposes
		\item What’s an easy way to stay EMC compliant?
		Stay below \( 1kV \) and below an RF power of \( 3.5 \unit{W} \)
		\item Why do you want/need the CE sticker?
		In the EU yes
		\item How long should you store all product-relevant documentation?
		10 Years
		\item What is the best/most convenient incoterm for the selling company?
		Xworks, as soon as the product leaves your door its no longer your liability
	\end{itemize}

\end{document}
